\subsubsection{President}
\label{president}

The President shall:

\begin{enumerate}
 \item
  Be ultimately responsible for maintaining the integrity of the MES.
 \item
  Enforce compliance with the Constitution, By-laws, Policy Manual, and regulations of the MES.
 \item
  Supervise all activities of the MES and its affiliated committees.
 \item
  Responsible for assisting in the development of goals for MES Team members, and actively tracking those goals for the duration of their term.
 \item
  Serve as a MES representative on the following committees:

  \begin{enumerate}
   \item
    President's Council of the McMaster Students Union (MSU)
   \item
    Faculty of Engineering Committees (Faculty committee)
   \item
    macLAB Board of Directors
  \end{enumerate}
 \item
  Serve as an MES representative on external undergraduate engineering organizations' Presidents' meetings, including:

  \begin{enumerate}
   \item
    Canadian Federation of Engineering Students (CFES)
   \item
    Engineering Student Societies' Council of Ontario (ESSCO)
  \end{enumerate}
 \item
  Be an ex-officio member of all standing MES Committees, except those to which they have been duly appointed.
 \item
  Responsible, in the absence of VPSL, for approving any activities on behalf of the MES and ensuring the activities comply with University Health and Safety..
 \item
  Serve as a secondary signing officer, in conjunction with VPSL, or primary signing officer in the absence of the VPF, for the approval or creation of financial decisions.
 \item
  Arrange and facilitate monthly meetings with the Dean of Engineering to ensure each party is familiar with relevant issues and activities.
 \item
  Ensure MES Board of Advisors meetings are held bi-annually
 \item
  Be responsible for selecting President's Award recipient(s) and presenting the President's Award to recipients at Fireball
 \item
  Actively promote interaction and communication between the MES, MES Clubs and Teams, MSU, the Engineering Student Representative Assembly caucus and Senate Representatives.
 \item
  Supervise the following positions:

  \begin{enumerate}
   \item
    Vice President, Academic
   \item
    Vice President, External Relations
   \item
    Vice President, Finance
   \item
    Vice President, Student Life
   \item
    Vice President, Communications
   \item
    Vice President, Internal
   \item
    Chief Returning Officer
   \item
    Co-Orientation Coordinators
   \item
    Equity, Diversity and Inclusion Officer
   \item
    First Year Council Coordinator
    \item
    MESSCO Coordinator(s)
   \item
    Program Representatives
   \item
    Pitch Your Own Idea Coordinators
  \end{enumerate}
 \item
  The President shall at their discretion delegate successful Pitch Your Own Idea Coordinators to relevant VP and Director portfolios.
 \item
  Develop both a short and long-term plan to encourage new initiatives and uphold traditional activities, as well as reviewing the current activities of the MES.
 \item
  Be responsible for the long term plan

  \begin{enumerate}
   \item
    Facilitate the implementation of the long term plan strategies
   \item
    Facilitate the collections of the long term plan metrics
   \item
    Develop new strategies and metrics with the MES Team and the Board of Advisors
  \end{enumerate}
\end{enumerate}