 \subsubsection{Vice President,
 Internal}
\label{vice-president-internal}
The Vice President, Internal shall:

\begin{enumerate}
 \item
  Oversee all MES administrative platforms and accounts, as well as the foundation and upkeep of MES infrastructure.
 \item
  Oversee upkeep and renewal of the online platforms of the MES, including Google Workspace, Microsoft Teams, Discord, website hosting, and domain registration.
 \item
  Oversee maintenance, organization, and use of all physical MES spaces, including, but not limited to:

  \begin{enumerate}
   \item
    H202 (MES Office)
   \item
    H206 (Clubs \& Teams Space)
   \item
    H201, H203, H204A/B, H205 (Hatch Meeting Rooms)
   \item
    H103 (Hatch Storage Room)
   \item
    JHE-195A (Basement Storage Room)
   \item
    Junction (2nd Floor Hatch)
   \item
    DW Lounge
  \end{enumerate}
 \item
  Oversee storage and use of all MES assets, including rentals.
 \item
  Supervise and act on internal matters such as communication, transition and reports.
 \item
  Determine the allocation of Hatch space to Clubs and Teams demonstrating essential need, including, but not limited to, sea can storage, Hatch Bay space, Clubs \& Teams Office desks and lockers, and H103 storage space.
 \item
  Collaborate with the Administrator to schedule meeting times for General Meetings, Council Meetings, and other meetings that arise.
 \item
  Organize, alongside the Administrator, the General Meetings of the MES.
 \item
  Take and distribute minutes and agendas for all MES Executive Meetings and MES Executive-Director Meetings. Send Executive minutes to the MES Executive by the end of the week in which the meeting occurred.
 \item
  Liaise with University Health and Safety and ensure all MES and Program Society social activities abide by its guidelines.
 \item
  Report to the President
 \item
  Supervise the following positions:

  \begin{enumerate}
   \item
    Administrator
   \item
    Director of Clubs
   \item
    DW Lounge Coordinator(s)
   \item
    Gerald Hatch Centre Student Coordinator(s)
   \item
    Information Technology Coordinator(s)
   \item
    Trailer Coordinator(s)

  \end{enumerate}
\end{enumerate}