\subsubsection{Vice President,
 Academic}
\label{vice-president-academic}
The Vice President, Academic shall:

\begin{enumerate}
 \item
  Develop and facilitate academic partnerships both internal and external to the MES.
 \item
  Liaise with Faculty, Program Representatives, Program Societies, and Faculty of Engineering undergraduate students regarding educational and academic issues.
 \item
  Chair the MES Academic Affairs Council Internal, which is facilitated as a monthly meeting featuring Program and First Year Representatives.
 \item
  Liaise with the SRA and/or Senate Representatives with regards to relevant university issues such as tuition, course evaluations, and program changes.
 \item
  Actively investigate educational and academic issues for Faculty of Engineering undergraduate students.
 \item
  Be responsible for recruitment issues and initiatives in coordination with the Vice President External Relations.
 \item
  Maintain the MES Tutoring Network and ensure it follows the expectations outlined in MES Bylaws Section \ref{mes-tutoring-network}
 \item
  Initiate and/or review changes to course evaluations.
 \item
  Be aware of and discuss relevant accreditation issues.
 \item
  Represent the MES at any accreditation visits or send an appropriate delegate in their place.
 \item
  Attend MSU Academic Affairs Council.
 \item
  Serve on the Faculty Committee as well as any education - related faculty committees.
 \item
  Serve on any educational ad-hoc MES committees.
 \item
  Organize the MES First Year Stream Information Session, where first years can come and talk to upper year students regarding their program.
 \item
  Be an ex-officio member of the McMaster Engineering Competition Committee (see MES Bylaws Section \ref{mcmaster-engineering-competition-committee}).
 \item
  Assist MEC Chair(s) in promoting participation of the student body in MEC (see MES Bylaws Section \ref{mcmaster-engineering-competition-chairs} and \ref{mcmaster-engineering-competition-committee}).
 \item
  Organize Back2School Week following Welcome Week, with assistance from the VPSL.
 \item
  Organize the Iron Pin Ceremony with First Year Committee.
 \item
  Report to the President.
 \item
  Supervise the following position:

  \begin{enumerate}
   \item
    McMaster Engineering Competition Chair(s)
   \item
    macLAB Chair
   \item
    Mentorship Coordinator(s)
   \item
    Director of Academic Resources
   \item
    Professional Development Coordinator(s)
   \item
    Student Projects Coordinator(s)

  \end{enumerate}
\end{enumerate}