\section{Services}
\label{services}

\subsection{Publications}
\label{publications}

\subsubsection{Approval}
\label{approval}
All material published in the Plumbline, Frequency and Engineering
Handbook must first get unanimous approval from the Editorial Review
Committee (see MES Bylaws Section \ref{editorial-review-committee}).

\subsubsection{Purpose}
\label{purpose}
The purpose of an MES publication is:

\begin{enumerate}
 \item
  To provide a means of communication for the MES.
 \item
  To provide information to the engineering students at McMaster University.
 \item
  To provide news and feature coverage of campus and/or engineering related events.
 \item
  To provide a forum through which students can express their concerns or opinions.

\end{enumerate}

\subsubsection{Editorial Policy}
\label{editorial-policy}
Material considered for publication must be consistent with the above
purposes and the following editorial policy:

\begin{enumerate}
 \item
  Any material submitted to these publications is considered for publication if, in the opinion of the editors, it is:

  \begin{enumerate}
   \item
    A paid advertisement or classified listing.
   \item
    A feature dealing with engineering-related issues.
   \item
    A message from the MES Team or Executive.
   \item
    An editorial or letter to the editors.
   \item
    A feature coverage of a campus and/or engineering-related event.
   \item
    A message from Engineering Co-op and Career Services.
   \item
    A humorous piece for entertainment purposes.
  \end{enumerate}
 \item
  Material considered for publication will NOT be printed if, in the opinion of the Editor(s) or the Editorial Review Committee, it is:

  \begin{enumerate}
   \item
    RACIST. Racist material is any material deemed to explicitly or implicitly defame or discriminate against any person or group on the basis of their ethnic, national, or religious background.
   \item
    SEXIST. Sexist material is any material judged to explicitly or implicitly promote gender inequality, indicate sexual bias or imply discrimination on the basis of gender.
   \item
    HOMOPHOBIC. Homophobic material is any material judged to explicitly or implicitly defame or discriminate against any specific person or group on the basis of their (perceived) sexual orientation, or be based upon hatred and/or intolerance of homosexuals or homosexual culture.
   \item
    LIBELLOUS. Libellous material is any material that unfairly defames any person's character or reputation through innuendo or falsehood.
   \item
    PORNOGRAPHIC. Pornographic material is any material judged to be erotic or sexual nature intended to excite prurient feelings.
  \end{enumerate}
 \item
  The use of vulgar language will be limited to the Plumbline and the Engineering Handbook. Vulgar language will be limited to those colloquialisms commonly found in the average university student's vocabulary.
 \item
  All other areas not specifically covered by this policy are left to the discretion of the Editor(s) and the Editorial Review Committee.
 \item
  If the occasion arises where an article is printed and distributed which the Dean of Engineering deems unacceptable for reading, the paper must immediately be retracted. In this case, at least 80\% of the publication must be collected.
 \item
  Any complaints about the contents of one of the publications of the MES shall be handled in the following manner:

  \begin{enumerate}
   \item
    The MES VPC must be contacted and informed of the specific concerns and problems.
   \item
    All valid complaints will receive a response within two weeks and an invitation to meet with the MES President and the Editorial Review Committee.
   \item
    If the situation is not resolved at this point, a meeting will be set with the Dean of Engineering, the MES President, and the Editorial Review Committee to discuss appropriate actions.
   \item
    If at any point it is felt that a formal apology or any such action is warranted, one will be sent to the complainant and published in the next issue of the publication.

  \end{enumerate}
\end{enumerate}

\subsubsection{Plumbline}
\label{plumbline}
The Plumbline is the McMaster Engineering Society's humorous student
publication.

\begin{enumerate}
 \item
  Printing and Distribution

  \begin{enumerate}
   \item
    Printed in newspaper format, it may contain student pictures, jokes, etc. selected by the Plumbline Editor(s).
   \item
    Issue distribution should be scheduled at least twice a semester, pending time and budget constraints.
   \item
    The Plumbline Editor(s), Publications Editor, and the VPC should decide on the number of papers printed.
   \item
    The paper should be distributed through the DW Lounge.
   \item
    The entire contents of each Plumbline must be reviewed by the Editorial Review Committee to ensure the contents strictly fall within the guidelines of the Editorial Policy (see MES Bylaws Section \ref{editorial-review-committee} and \ref{editorial-policy}). % fix this lol - MES Policy Manual Section B.1.3, verify correct adjustment
   \item
    The Plumbline must be given to the Editorial Review Committee one week prior to being sent to print. The Plumbline can only be sent for print once the Plumbline Editor(s) have received a response from the majority of the Editorial Review Committee.
  \end{enumerate}
 \item
  Disclaimer Policy

  \begin{enumerate}
   \item
    The contents of the paper must include a disclaimer that explains to all readers that the articles are for entertainment purposes only, and are not intended to offend any person or party.
   \item
    A similar disclaimer should be given to sponsors to make them aware of the paper's contents.
   \item
    If student pictures or names are being used, the Plumbline Editor(s) must obtain the written permission of the student(s).

  \end{enumerate}
\end{enumerate}

\subsubsection{Frequency}
\label{frequency}
The Frequency is a serious publication that includes information
regarding upcoming academic and social events or announcements of the
MES and affiliated clubs and teams. Material from other groups can be
included, space permitting. Inappropriate pictures such as pictures of
substance consumption/abuse will not be printed in the Frequency.

\begin{enumerate}
 \item
  Publishment and Distribution

  \begin{enumerate}
   \item
    The Frequency is published quarterly (twice a semester) of the academic year.
   \item
    The number of copies printed is left at the discretion of the Frequency Editor(s), Publications Editor, and the VPC.
   \item
    Distribution should occur via the MES website, social media, and MES representatives.
   \item
    An additional supply of the Frequency should be placed in the DW Lounge, Engineering Alumni Office, Associate Dean's Office, and outside of Engineering Co-op and Career Services.

  \end{enumerate}
\end{enumerate}

\subsubsection{Engineering Handbook}
\label{engineering-handbook}
The Engineering Handbook is a publication primarily targeted to first
year engineering students with the intention of introducing them to
McMaster Engineering culture, while providing them with a humorous and
useful agenda booklet.

\begin{enumerate}
 \item
  Printing and Distribution

  \begin{enumerate}
   \item
    The Handbook Editor(s) shall ensure that the Handbook is ready for distribution during Welcome Week.
   \item
    The Handbook Editor(s), Publications Editor, and the VPC shall decide the number of Handbooks to be printed, provided that at least enough copies are printed to provide one to each first year student.
   \item
    Extra copies shall be distributed to upper level students.
  \end{enumerate}
 \item
  The Handbook should include the following components:

  \begin{enumerate}
   \item
    Front and back laminated covers, illustrated in colour
   \item
    MES Team email and position list
   \item
    MES Executive introductions
   \item
    Class schedule for each term
   \item
    Monthly calendars
   \item
    Daily planners with MES events printed on appropriate dates
   \item
    List and description of MES committees and sign up procedures
   \item
    Page for contact listings
   \item
    Jokes, poems, drawings, engineering traditions
   \item
    On and off-campus advertisements
   \item
    Coupons
   \item
    Annual MES award information
   \item
    Introduction to the MES
   \item
    List and description of all MES Awards
  \end{enumerate}
\end{enumerate}

\subsection{Website}
\label{website}
The MES website acts as a source of information for the McMaster
Engineering student body and those interested in our faculty. With that
in mind, the following points should be followed with respect to the
website.

\begin{enumerate}
 \item
  The Website Coordinator(s) is responsible for creating and maintaining the website.
 \item
  The Information Technology Coordinator(s) is responsible for resolving technical issues surrounding the website and ensuring website uptime.
 \item
  The language throughout the website should be clean and appropriate.
 \item
  There shall be no pictures of substance consumption/abuse or people committing inappropriate acts.
 \item
  Images that could be used for blackmail purposes will not be posted.
 \item
  If requested by any party, specified images must be removed promptly and without question.
 \item
  The website should have an up to date repository of all MES documents (Constitution, Bylaws, Policy Manual, meeting minutes, Plumbline, Frequency, Reports, etc.) and event news.
 \item
  Website editing access will be limited to the President, MES Executive, Website Coordinator(s), and Information Technology Coordinator(s). Further access may be granted at the discretion of the VPC.

\end{enumerate}

\subsection{DW Lounge}
\label{dw-lounge}
The David Wilkinson Undergraduate Engineering (DW) Lounge is for the use
of undergraduate engineering students only. It is thus the
responsibility of the Society to maintain the room in an orderly way.

\subsubsection{Facilities and Services}
\label{facilities-and-services}

\begin{enumerate}
 \item
  The following shall be provided in the DW Lounge:

  \begin{enumerate}
   \item
    Microwave
   \item
    Couches, chairs, tables, whiteboards with markers
   \item
    Access to Project Magazine and Engineering Dimensions
   \item
    Mailboxes for MES Team members
  \end{enumerate}
 \item
  Rules of Conduct

  \begin{enumerate}
   \item
    Students are expected to behave appropriately.
   \item
    Vandalism is not permitted.
   \item
    Students are permitted to eat in the lounge, but are responsible for the clean up of their own food.
   \item
    Notices of these rules and regulations should be posted in the DW Lounge.
  \end{enumerate}
 \item
  All facilities shall be maintained and kept in working order by the DW Lounge Coordinator(s) (see MES Bylaws Section \ref{dw-lounge-coordinators}).
\end{enumerate}
\subsection{Drain}
\label{drain}

The Drain is the store of the MES. It is the main distribution outlet for McMaster Engineering paraphernalia, tickets to events, and any other items sold on behalf of the MES. The Drain Coordinator(s) are responsible for daily operation of the Drain (see MES Bylaws Section \ref{drain-coordinators}).

\subsubsection{Staffing Policies}
\label{staffing-policies}

\begin{enumerate}
 \item
  Hiring

  \begin{enumerate}
   \item
    It is the Drain Coordinator's responsibility to recruit responsible and reliable volunteers to staff the Drain.
   \item
    The Drain Coordinator(s) should select students from different years if possible.
   \item
    All students selected by the Drain Coordinator(s) must sign a contract prior to working in the Drain (see MES Policy Manual Section G.A). % appendix - wtf? G.A??? how tf is that a thing
   \item
    All Drain volunteers must hold a MES membership throughout the duration of their term, unless a financial need exemption is granted at the discretion of the Chief Returning Officer.
  \end{enumerate}
 \item
  Training

  \begin{enumerate}
   \item
    It is the sole responsibility of the Drain Coordinator(s) to educate and train the volunteers. There will be an employee training session offered by the Drain Coordinator(s) which outlines the procedures involved with selling items, and proper sales etiquette and time commitments.
  \end{enumerate}
 \item
  Staff Responsibilities

  \begin{enumerate}
   \item
    Each volunteer is responsible to appear for their shift at their scheduled time. If any volunteer cannot appear during their time, the volunteer must give at least 24 hours notice to the Drain Coordinator(s) outlining the reason they can not make it. If there is no reason given, the volunteer is given a warning. Volunteers may be removed from the staff if this is a recurring event at the discretion of the Drain Coordinator(s).
  \end{enumerate}
\end{enumerate}

\subsubsection{Theft Policy}
\label{theft-policy}
Regarding any theft of items from the Drain, the following actions must
be taken:

\begin{enumerate}
 \item
  All volunteers working that day should be informed of the theft.
 \item
  The Drain Coordinator(s) is responsible for finding the person or persons involved in the theft. If the guilty party is not found, the Drain Coordinator(s) must refer to the inventory check sheet.
 \item
  The Drain Coordinator(s) must report any thefts directly to the President and VPF
 \item
  To reduce the amount of theft that can occur, only \$200 is allowed to remain in the drain overnight. The Drain Coordinator(s) is responsible to coordinate with the VPF to put any additional money in the safe.
\end{enumerate}

\subsubsection{Pricing}
\label{pricing}
The goal of the Drain is not to make a tangible profit towards the MES,
but rather to provide a service to the engineering students. For this
reason, prices do not have to be increased from the wholesale value by a
large amount. It is left at the discretion of the Drain Coordinator(s)
and VPF how much to mark up or discount each item.

\subsubsection{Advertising Policy}
\label{advertising-policy}
\begin{enumerate}
 \item
  All advertising must be developed and approved by the VPC.
 \item
  There must be no degradation of other faculties, professors, students or university staff.
 \item
  There is to be no false advertising. It should be indicated in the ad that a sale is valid ``while quantities last.''

\end{enumerate}

\subsubsection{Access Cards}
\label{access-cards}
Only the following people will have access cards to get into the Drain:

\begin{enumerate}
 \item
  President
 \item
  Vice President, Finance
 \item
  Vice President, Academic
 \item
  Vice President, Internal
 \item
  Drain Coordinator(s)
 \item
  The Co-Orientation Coordinators (From April of each year until 2 week after Welcome Week) % clerical
 \item
  Director of Events
 \item
  Director of Academic Resources

\end{enumerate}

\subsubsection{Student Organizations Merchandise}
\label{student-organizations-merchandise}
Engineering student organizations wishing to sell items through the
Drain must contact the Drain Coordinator(s) for authorization. This
service will be strictly limited to MES Clubs and Teams. Item sales are
separated into three categories: pre-orders \& event tickets, small
merchandise, and large merchandise.

\begin{enumerate}
 \item
  Merchandise pre-orders and event tickets are characterized by not requiring any physical merchandise to be kept in the Drain.

  \begin{enumerate}
   \item
    Student organizations wishing to sell merchandise pre-orders or event tickets through the Drain must send the Drain Coordinator(s) a detailed email describing the merchandise/event, pricing, number to be sold, and a link to a form for customers to fill out. This email must be sent a minimum of 2 weeks before sales begin.
   \item
    The Drain will then sell said merchandise pre-order or event ticket for a maximum of 2 weeks unless specific permission is granted by the Drain Coordinator(s).
   \item
    The Drain is not responsible for the distribution of the pre-ordered merchandise once it arrives, unless separate authorization of small or larger merchandise is given.
   \item
    Revenue shall be reimbursed by the VPF no more than one month after sales finish.
  \end{enumerate}
 \item
  Small merchandise is characterized by requiring minimal storage space and includes patches, stickers, pins, lanyards, stickers, and other such items.

  \begin{enumerate}
   \item
    Student organizations wishing to sell small merchandise through the Drain must fill out the Drain Club Merchandise Form and send it to the Drain Coordinator(s) (see MES Policy Manual Section G.W).
   \item
    The merchandise will be placed in the display and sold the same way as all regular merchandise.
   \item
    Revenue shall be reimbursed by the VPF semi-annually until there are no more items remaining.
  \end{enumerate}
 \item
  Large merchandise is characterized by requiring a significant amount of storage/display space. This includes shirts, hoodies, hats, and other such merchandise.

  \begin{enumerate}
   \item
    Large merchandise will generally not be taken due to lack of storage and display space.
   \item
    Exceptions may be made for more ``general'' engineering merchandise - merchandise which is not specific to one single student organization. This is at the discretion of the Drain Coordinator(s) and VPF.
   \item
    If an exception is granted, the merchandise must be processed in the same fashion as small merchandise.
  \end{enumerate}
 \item
  Merchandise pick-up is characterized by student group swag that has been pre-ordered for individuals.

  \begin{enumerate}
   \item
    The timeline and duration of the merchandise pick-up will be decided at the discretion of the Drain Coordinator(s).
  \end{enumerate}
\end{enumerate}

\subsection{MES Office}
\label{mes-office}

\subsubsection{Office Use}
\label{office-use}

The MES Office is for the use of the following MES Team members only:

\begin{enumerate}
 \item
  All MES Executive members
 \item
  All Directors
 \item
  Frequency Editor(s)
 \item
  Plumbline Editor(s)
 \item
  Handbook Editor(s)
 \item
  Information Technology Coordinator(s)
 \item
  Drain Coordinator(s)
 \item
  The Co-Orientation Coordinators
 \item
  Administrator
 \item
  Equity and Inclusion Officer
 \item
  Chief Returning Officer
 \item
  Publications Editor
 \item
  Gerald Hatch Centre Student Coordinator(s)
 \item
  All Program Representatives
 \item
  The Welcome Week Orientation Planning Committee (from May until the day before the first day of classes)
\end{enumerate}

\subsubsection{Keys, Security and Auxiliary Access}
\label{keys-security-and-auxiliary-access}
\begin{enumerate}
 \item
  The MES office is secured with a keycard lock for which only the above MES Team members will be given keycard access to.
 \item
  It is the Responsibility of the Vice-President, Internal to assign and revoke keycard access to the MES Office.
 \item
  Under special circumstances, other MES Team members who request use of the office for MES Team activities may also be issued provisional access by one of the members listed in the MES Policy Manual Section B.6.1.
 \item
  Any MES members currently serving on Engineering Student Societies' Council of Ontario or Canadian Federation of Engineering Students may be given limited access for business of their position only. This request must be approved by the MES Executive.
 \item
  A contract must be signed by all office users to ensure that all rules pertaining to the MES Office are followed (see MES Policy Manual Section G.V) and must be submitted to the Administrator. % fix this lol

\end{enumerate}

\subsubsection{Etiquette and Housekeeping}
\label{etiquette-and-housekeeping}
\begin{enumerate}
 \item
  Each user of the office is responsible for cleaning up after themselves. This includes disposing of scrap paper and food, recycling appropriate materials, wiping off desks and the productions computer, and securely locking the door.
 \item
  At the beginning of the school year, at the end of each semester, and at the end of their term of office, the Administrator will conduct an inventory check of the office to ensure archived material is not lost and to check for theft. The MES is not accountable for items not belonging to MES.

\end{enumerate}

\subsubsection{Office Equipment}
\label{office-equipment}
\begin{enumerate}
 \item
  The MES Office contains one computer, printer, and stationary supply. The computer contains word-processing, spreadsheet, and design software for MES-related work including typing meeting minutes, creating posters, designing newspaper layouts, etc.
 \item
  The Information Technology Coordinator(s) is responsible for the installation and maintenance of office equipment.
 \item
  Only the Information Technology Coordinator(s) is authorized to install software on the computer.
 \item
  Any MES activities take priority over the use of the computer for personal business.
 \item
  Stationary is purchased as needed by the Administrator for the printer and for MES work only.

\end{enumerate}

\subsection{MES Trailer}
\label{mes-trailer}
The MES Trailer is property of the MES. It is available for use by any
recognized MES Group or MES member and shall be administered by the
Trailer Coordinator(s). No modifications (including applying decals to
the exterior) shall be made to the MES Trailer without prior consent
from the Trailer Coordinator(s) and the MES Executive.

\subsubsection{Bookings}
\label{bookings}

\begin{enumerate}
 \item
  All bookings must be made at least one week in advance.
 \item
  The Trailer Coordinator(s) will organize bookings.
 \item
  One person in the group booking the MES Trailer must sign a contract of liability.
 \item
  The group booking the MES Trailer must provide information about the driver, vehicle that will be towing the MES Trailer, and proof of insurance for towing a trailer.
 \item
  The group booking the MES Trailer is responsible for cleaning up any mess left in or on the MES Trailer. Failure to do so may result in a \$50 fine, at the discretion of the Trailer Coordinator(s) and the MES Executive.
 \item
  Any articles left in the MES Trailer become property of the MES if they are not claimed within one week of the MES Trailer being returned.

\end{enumerate}

\subsubsection{Keys}
\label{keys}
\begin{enumerate}
 \item
  There shall be three sets of keys to the MES Trailer, one of which will be held by the VPF and the other two will be held by the Trailer Coordinator(s).
 \item
  Keys can be picked up by the group who has the MES Trailer booked no more than two days before their scheduled booking period.
 \item
  All keys to the MES Trailer must be returned to the Trailer Coordinator(s) within two days after the scheduled booking period has ended.
 \item
  No additional copies of the MES Trailer keys may be made, except by the Trailer Coordinator(s) with written permission from the MES Executive. If illegal copies are found, the offending party will be subject to loss of privileges or other punishment as recommended by the MES Executive.

\end{enumerate}

\subsubsection{Use of Trailer}
\label{use-of-trailer}
All borrowers of the MES Trailer must comply with the MES Trailer Usage
Guidelines and sign the MES Trailer Use Contract and submit it to the
Trailer Coordinator(s) (see MES Policy Manual Section G.G). % fix this lol - more references

\subsubsection{Damage}
\label{damage}

\begin{enumerate}
 \item
  Any damage to the MES Trailer must be reported to the Trailer Coordinator(s) immediately.
 \item
  Groups or individuals borrowing the MES Trailer may be held responsible for any damage incurred during its use.
 \item
  Only the Trailer Coordinator(s) is authorized to perform or sanction any type of repair on the MES Trailer.
 \item
  If a group has not taken proper action in the event of damage and inconveniences another group's ability to follow through with their own booking, a minimum of \$100, or 10\% of the damage cost (whichever is greater) inconvenience fee will be imposed upon the group.

\end{enumerate}

\subsection{MES Equipment Rental}
\label{mes-equipment-rental}
The MES offers many different types of equipment for rental to MES
students and MES student groups. The full list of equipment is
summarised below: % fix this lol - just fucked up honestly

\begin{enumerate}
 \item
  Projector (see MES Policy Manual Section G.I)
 \item
  DSLR Camera (see MES Policy Manual Section G.J)
 \item
  Tent (see MES Policy Manual Section G.K)
 \item
  Wireless Radios (see MES Policy Manual Section G.L)
 \item
  Water Coolers \& Coffee Urns (see MES Policy Manual Section G.R)
 \item
  Button Maker (see MES Policy Manual Section G.T)
\end{enumerate}

\subsection{Storage Room}
\label{storage-room}

Only the President, VPI, and both of the Co-OCs shall have access to the basement storage room (JHE-195A). The Co-OCs shall return this key by the second Friday following Welcome Week.

\subsection{McMaster Peer Tutoring Program}
\label{mcmaster-peer-tutoring-program}

The McMaster Peer Tutoring Program is a program developed to help McMaster Engineering students excel in their studies at McMaster and to create part-time employment opportunities for potential tutors. All aspects of this program will be managed by the Student Success Centre and the VPA.

\subsubsection{MES Tutoring Network}
\label{mes-tutoring-network}

\begin{enumerate}
 \item
  The McMaster Peer Tutoring Program is a program developed to provide McMaster students access to academic assistance through the provision of tutors for courses at McMaster at an affordable price. The MES is to maintain its partnership with the Student Success Centre unless the MES no longer benefits from the relationship. The MES Tutoring Network is a subset of the McMaster Peer Tutoring Program offered by the Student Success Centre. The MES Tutoring Network is designed to encourage peer-to-peer academic support by offsetting the cost of tutoring sessions between MES members. The VPA is responsible for maintaining the MES' relationship with the Student Success Centre to upkeep the Tutoring Network as long as the relationship is beneficial to the MES membership, and it follows the following expectations of the MES Tutoring Network:

  \begin{enumerate}
   \item
    The entirety of the monetary sponsorship of the program the MES provides shall be applied directly to reducing the cost of tutoring costs for MES members.
   \item
    Both the tutee and the tutor in a MES sponsored session must be MES members.
   \item
    There must exist a reasonable limit to the monetary value which any one tutee can take out of the system
  \end{enumerate}
 \item
  Online Coupons

  \begin{enumerate}
   \item
    The VPA will ensure that all MES members pay no more than \$5 per coupon, up to a limit of 10 per student per academic term
   \item
    More than one voucher may be redeemed per session with a tutor
   \item
    Tutors must be able to earn no less than the minimum wage rate in Ontario.
   \item
    Online Coupons can only be purchased by McMaster Undergraduate students in Faculty of Engineering for personal use.
  \end{enumerate}
 \item
  Tutors

  \begin{enumerate}
   \item
    Must be registered with the MES to be recognized as an MES tutor
   \item
    Must have received a grade of 10 or higher in a course to be able to qualify to be a tutor for that course
   \item
    There is no limit to the number of redeemable vouchers for tutors
  \end{enumerate}

\end{enumerate}

\subsection{MES Textbook Library}
\label{mes-textbook-library}
The MES Textbook Library is a service provided by the MES to provide
McMaster undergraduate students in the Faculty of Engineering with
textbooks for free. The MES Textbook Library shall be run out of the
Drain and shall be maintained by the DoAR.

\subsubsection{Operation}
\label{operation}

\begin{enumerate}
 \item
  The MES Textbook Library shall be run out of the Drain during regular operating hours.
 \item
  When an individual signs out a textbook, the Drain volunteer must record the individual's McMaster email along with the identification of which textbook is signed out.
 \item
  All textbooks shall be returned to the Drain before the Drain's last operating hours of a semester.
 \item
  If a textbook is outstanding past the end of the semester, the individual who signed out the account shall be charged a \$100 fine to their student account, unless otherwise arranged with the DoAR.

\end{enumerate}

\subsection{MES Academic Workshops}
\label{mes-academic-workshops}

\subsubsection{MES-Organized
 Workshops}
\label{mes-organized-workshops}
\begin{enumerate}
 \item
  The MES runs academic and technical workshops for general first year and second year engineering courses. The DoAR is responsible for organizing workshops, finding workshop leads (upper year students), and paying them.
 \item
  Workshop leads shall be paid at a rate of \$27/hour, up to a maximum of 3 hours per workshop.
 \item
  Workshop leads must complete Appendix Y and submit it to the DoAR in order to be reimbursed.
 \item
  Workshop leads shall not be teaching assistants for courses they are organizing workshops for.
\end{enumerate}

\subsubsection{Program-Society-Organized Academic
 Workshops}
\label{program-society-organized-academic-workshops}
\begin{enumerate}
 \item
  Program Societies may run their own academic workshops for department-specific courses. Program Societies are responsible for organizing workshops and finding workshop leads, and paying them.
 \item
  All Program societies shall submit for prior approval from the DoAR, at least 2 weeks prior to any eligible academic workshops which they would request funding.
 \item
  Workshop leads shall be paid at a rate of \$27/hour, up to a maximum of 3 hours per workshop and 1 help session lead per workshop.
 \item
  MES Program representatives are responsible for ensuring that their workshop leads complete Appendix Y and for submitting it to the DoAR in order for their Program Society to be reimbursed.
\end{enumerate}

\subsection{Coveralls}
\label{coveralls}
Coveralls are worn by undergraduate engineering students to represent
the Faculty of Engineering. The coveralls are a well-known symbol within
the University, the Hamilton area, and engineering schools across the
province and country. The coveralls have a complex, deep-rooted history.
The coverall approval process ensures that the coveralls are worn by
those who understand the significance of the coverall and the
responsibility that comes with wearing the coverall.

\subsubsection{Coverall Oversight Committee}
\label{coverall-oversight-committee}

\begin{enumerate}
 \item
  The Coverall Oversight Committee is responsible for:

  \begin{enumerate}
   \item
    Ensuring the coveralls are positively representing the Faculty of Engineering
   \item
    Reviewing and approving Coverall Sponsor applications
   \item
    Reviewing and approving Coverall Event applications
   \item
    Reviewing and approving Coverall applications
   \item
    Rescinding Coverall Sponsor and Coverall Event approval
   \item
    Evaluating infringements and consequences for individuals who break the Sponsor Contract, Coverall Usage Contract, and Coverall Code of Conduct.
  \end{enumerate}
 \item
  The Coverall Oversight Committee will be chaired by the Vice-President External.
 \item
  The voting membership of the Coverall Oversight Committee shall consist of:

  \begin{enumerate}
   \item
    President
   \item
    Vice-President, Student Life
   \item
    Co-Orientation Coordinators
    \begin{enumerate}
     \item
      The term is their Welcome Week calendar year (January - December)
    \end{enumerate}
   \item
    Equity, Diversity, and Inclusion Officer
  \end{enumerate}
 \item
  All decisions of the committee must be unanimous.
\end{enumerate}

\subsubsection{Responsibilities}
\label{coverall-responsibilities}
\begin{enumerate}
 \item
  The Vice-President, External is responsible for:
  \begin{enumerate}
   \item
    Overseeing and being ultimately responsible for the coveralls.
   \item
    Track the inventory of coveralls and organize future orders of coveralls.
   \item
    Collaborate with the Drain Coordinators on the purchase and distribution of coveralls.
   \item
    Coordinating sizing, pick-up, and payment with approved applicants during regular Drain operating hours in order for the Drain volunteers to facilitate payment.
   \item
    Maintaining and updating the Coverall Sponsor, Coverall Event, and Coverall Application forms.
   \item
    Collecting a list of individuals attending the Coverall Event from the Coverall Sponsor.
   \item
    Ensuring the voting members of the Coverall Oversight Committee review applications on a regular basis.
   \item
    Communicating application status with Coverall Sponsors and the application status of their Coverall Event(s).
   \item
    Maintaining a list of club executives, vetting the eligibility of Coverall Sponsor applicants, and acting as the Coverall Sponsor in the case a Coverall Sponsor applies to purchase Coveralls for their own Coverall Event.
   \item
    Communicating application status with Coverall Applicants.
   \item
    At their discretion, appoint and oversee a Chair and delegate responsibilities to the Chair.
  \end{enumerate}
 \item
  The Chair is responsible for:
  \begin{enumerate}
   \item
    Organizing meetings to further discuss applications, where necessary.
   \item Executing responsibilities as delegated by the Vice-President, External.
  \end{enumerate}
\end{enumerate}
\subsubsection{Coverall Sponsors}
\label{coverall-sponsors}

\begin{enumerate}
 \item
  Coverall Sponsors are individuals in the engineering community who act as sponsors for individuals who are applying for coveralls.
 \item
  Student leaders in MES Groups, Teams, Program Societies, Committees, and Affiliates (hereafter referred to as ``Student Organizations'') may apply to become a Coverall Sponsor.
 \item
  All Coverall Sponsors must submit a signed Coverall Sponsorship Usage Contract (Appendix Z) with their Coverall Event application.
 \item
  Upon approval of their Coverall Event, Coverall Sponsors must still fill out the Coverall Application if they are interested in purchasing their own coveralls.

\end{enumerate}
\subsubsection{Coverall Events}
\label{coverall-events}
\begin{enumerate}
 \item
  Coverall Events are events where the coverall will represent the Faculty of Engineering in a positive light.
 \item
  Coverall Event applications must be submitted by an individual meeting the criteria of a Coverall Sponsor as outlined in \ref{coverall-sponsors}.
 \item
  Coverall Event applications are required for all events where coveralls will be worn.
 \item
  Coverall Events need to be resubmitted each year, even for an event with the same name and purpose that was approved in a prior year.
 \item
  Coverall Events may be approved for either of the following purposes:
  \begin{enumerate}
   \item
    The wearing of coveralls at the Coverall Event
   \item
    The purchase of coveralls, which can then be worn at the Coverall Event
  \end{enumerate}
 \item
  Examples of eligible Coverall Events include, but are not limited to:

  \begin{enumerate}
   \item
    Welcome Week
   \item
    ESSCO and CFES Conferences
   \item
    Team competitions
   \item
    Contingents at a parade
  \end{enumerate}
 \item
  The Coverall Event application will consist of questions determined at the discretion of the Coverall Oversight Committee.
 \item
  Coverall Events will be approved or denied at the discretion of the Coverall Oversight Committee.

\end{enumerate}

\subsubsection{Coverall Applications}
\label{coverall-applications}
\begin{enumerate}
 \item
  The Coverall Application is required only for individuals who are interested in obtaining their own coveralls to represent the Faculty of Engineering at a Coverall Event (hereafter referred to as ``Coverall Applicants'').
 \item
  The Coverall Application Form will consist of the following:

  \begin{enumerate}
   \item
    Personal Information

    \begin{enumerate}
     \item
      Full Name
     \item
      McMaster Email
     \item
      Starting year at McMaster
     \item
      Program
     \item
      Proof of Enrolment
    \end{enumerate}
   \item
    Coverall Information

    \begin{enumerate}
     \item
      Coverall Event
     \item
      Sponsor Name
     \item
      Signed Coverall Usage Contract (Appendix AA)
     \item
      Signed Coverall Code of Conduct (Appendix AB)
    \end{enumerate}
   \item
    Proof of Training

    \begin{enumerate}
     \item
      Accessibility for Ontarians with Disabilities Act (AODA) and University Health \& Safety (UHS) Trainings

      \begin{enumerate}
       \item
        AODA and Human Rights Code
       \item
        Health and Safety Orientation
       \item
        Violence and Harassment Prevention
      \end{enumerate}
     \item
      It Takes All of Us (CONSENT 1A00)
     \item
      Responding to Disclosures on Campus
     \item
      More Feet on the Ground
    \end{enumerate}
  \end{enumerate}
 \item
  The Coverall Application may consist of additional questions and training determined at the discretion of the Coverall Oversight Committee.
 \item
  Coverall Applications will be cross-referenced with a list of individuals attending the Coverall Event.
 \item
  Coverall Applications will be approved or denied at the discretion of the Coverall Oversight Committee.
 \item
  Once approved, the Coverall Applicant will be contacted to coordinate sizing, pick-up, and payment.
 \item
  Engineering Welcome Week Representatives are exempt from the Coverall Application process, by virtue of the Welcome Week Representative recruitment process and the Student Success Centre Welcome Week Representative training.
  \begin{enumerate}
   \item
    Engineering Welcome Week Representatives are bound to all other regulations other than the Coverall Application process.
  \end{enumerate}
\end{enumerate}
