\section{Appointed Positions}
\label{appointed-positions}
\subsection{Appointed Positions}
\label{appointed-positions1}

The following positions are members of the MES Team, but do not have voting rights.

\subsubsection{DW Lounge Coordinator(s)}
\label{dw-lounge-coordinators}
The DW Lounge Coordinator(s) shall:

\begin{enumerate}
 \item
  Be responsible for monitoring the television and microwave at least three times a week to ensure no damage has occurred.
 \item
  Ensure the following activities will occur on a regular basis:

  \begin{enumerate}
   \item
    Expired posters will be taken down.
   \item
    Microwave will be wiped clean.
   \item
    Chairs and couches will be arranged neatly.
   \item
    Maintain lounge supplies.
  \end{enumerate}
 \item
  Carry out a complete cleaning of the DW Lounge at the end of each semester. This will entail dusting couch cushions, washing the floor, polishing furniture, cleaning the microwave and the windows, taking down expired decorations, and refreshing the air.
 \item
  Be responsible for all cleaning except for the duties of Facility Services staff. Facility Services is ONLY responsible for collecting garbage and recycling daily, as well as for sweeping and mopping the floor.
 \item
  Propose expenditures for the lounge budget.
 \item
  Report to the VP Internal.
 \item
  Be a position held by a maximum of two people.
\end{enumerate}

\subsubsection{Chief Returning Officer}
\label{chief-returning-officer}
The Chief Returning Officer shall:

\begin{enumerate}
 \item
  Act as an unbiased chair for MES Council Meetings and General Meetings.
 \item
  Maintain order and integrity in all MES Council Meetings and General Meetings in accordance with the MES Robert's Rules of Order (see MES Bylaws Section \ref{mes-roberts-rules-of-order}).
 \item
  Update the MES Policy Manual, Bylaws, and Constitution to reflect changes approved at MES General Meetings or Council Meetings.
 \item
  Coordinate all MES elections as outlined in MES Bylaws Section \ref{elections-selections}.
 \item
  Chair the Elections Committee (see MES Bylaws Section \ref{elections-committee-guidelines}).
 \item
  Chair the Awards Selection Committee (see MES Bylaws Section \ref{awards-selection-committee}).
 \item
  Meet eligibility criterias as outlined in MES Bylaws Section \ref{chief-returning-officer-eligibility}
 \item
  Report to the President.
 \item
  Be a position that must only be held by one person.
 \item
  Not hold any voting position within the MES Council.
\end{enumerate}

\subsubsection{Co-Orientation Coordinators}
\label{co-orientation-coordinators}
The Co-Orientation Coordinators shall:

\begin{enumerate}
 \item
  Meet eligibility criteria and be appointed by a selection committee as outlined in MES Bylaws Section \ref{co-orientation-coordinators-eligibility}.
 \item
  At least one of the Co-Orientation Coordinators must have previously served for at least one year on the Orientation Planning Committee
 \item
  Be familiar both with the MES and with the Engineering Welcome Week.
 \item
  Chair the Orientation Planning Committee and select its members (see MES Bylaws Section \ref{welcome-week-orientation-planning-committee}).
 \item
  Organize all events occurring during Welcome Week (See Policy Manual Special Events). % fix this ?
 \item
  Work with the President and VPC to create the Summer Mail-Out, the WW promotional campaign, and to develop a social media plan for WW.
 \item
  Submit a follow up report and evaluation of Welcome Week to both the MES and the Student Success Centre before the end of September.
 \item
  Attend or delegate core meetings and training sessions provided by the Student Success Centre.
 \item
  Report to the President.
 \item
  Be a position that must be held by two people.
\end{enumerate}

\subsubsection{Culture Coordinator(s)}
\label{culture-coordinators}
The Culture Coordinator(s) shall:

\begin{enumerate}
 \item
  Coordinate events with the DoE.
 \item
  Ensure that McMaster Engineering traditions are maintained.
 \item
  Build ties with engineering alumni and, if possible, organize speakers/speeches regarding McMaster Engineering culture and tradition when appropriate.
 \item
  Chair the Culture Committee (see MES Bylaws Section \ref{culture-committee}).
 \item
  Initiate and respond to any interuniversity prank with the approval of the MES President, faculty, and the ESSCO Rapscallions.
 \item
  Serve on the Student Life Committee, (see MES Bylaws Section \ref{student-life-committee}).
 \item
  Periodically suggest updates to the Culture section of the MES website.
 \item
  Responsible for organizing the following events;

  \begin{enumerate}
   \item
    Academic Flush
   \item
    Oksoberfest
   \item
    Santa Hog
   \item
    MES attendance at the Hamilton Santa Claus Parade
   \item
    MES Canada Day on the weekday closest to January 23rd
   \item
    Pi Day
   \item
    Movember Charity initiative
  \end{enumerate}
 \item
  Responsible for ensuring the continued operation of the Iron Ring Clock.
 \item
  Responsible for creating new culture items that will benefit the MES, in addition to maintaining past culture items, including:

  \begin{enumerate}
   \item
    Flush Toilet
   \item
    MES Podium
  \end{enumerate}
 \item
  Meet the eligibility criteria, as outlined in C.6.a % ?
 \item
  Report to the President.
 \item
  Be a position held by a maximum of three people.

\end{enumerate}

\subsubsection{Drain Coordinator(s)}
\label{drain-coordinators}
The Drain Coordinator(s) shall:

\begin{enumerate}
 \item
  Recruit a suitable staff of volunteers.
 \item
  Train all employees at the beginning of their term.
 \item
  Develop creative ideas for new apparel and merchandise.
 \item
  Organize times for the sale of leather jackets, and help the companies in charge of these items with the sales process, including receiving any deliveries.
 \item
  Collect and record all payments from students for the purchase of leather jackets.
 \item
  Keep accurate and regular records of inventory.
 \item
  Make cash deposits into the MES safe on a daily basis so that the cash in the Drain does not exceed \$200 at the end of each day, to a maximum of \$50 in coins and \$150 in cash.
 \item
  Ensure that all deposits in the MES safe are properly labelled with the source of income, amount, and date deposited.
 \item
  Be responsible for delegating the opening and closing of the Drain.
 \item
  Arrange for the Advertising Committee to promote sales and other campaigns.
 \item
  Consult with suppliers, students, and the VPF about upcoming campaigns (i.e. new paraphernalia).
 \item
  Keep the Drain neat and organized.
 \item
  Coordinate the sale of event tickets by Drain staff with the DoE.
 \item
  Keep a record of all sales (both ticket and item) made, via regular inventory checks and consolidating the Square sales records. A record of ticket sales is to be kept on the event sheet provided by the DoE.
 \item
  Report to the VPF.
 \item
  Be a position held by a maximum of three people.
\end{enumerate}

\subsubsection{Equity, Diversity and Inclusion Officer(s)}
\label{equity-diversity-and-inclusion-officers}
The Equity, Diversity and Inclusion Officer(s) shall:

\begin{enumerate}
 \item
  Provide specific equity consultations for Team members during the planning process of events and initiatives. Focus should be given to:

  \begin{enumerate}
   \item
    Accessibility
   \item
    Inclusion
   \item
    Diversity
  \end{enumerate}
 \item
  Provide general resources for MES Team members and MES clubs and teams to utilise when running events to ensure equity.
 \item
  Analyze and update MES policy to be equitable.
 \item
  Sits on the Election Committee (see MES Bylaws Section \ref{elections-committee}).
 \item
  Chair the I.D.E.A Committee (see MES Bylaws Section \ref{i.d.e.a.-committee-inclusivity-and-diversity-in-engineering-alliance}):
 \item
  Train the MES Team at the following meetings:

  \begin{enumerate}
   \item
    Big Team Meeting
   \item
    SAGM I
   \item
    SAGM II
  \end{enumerate}
 \item
  Build and run equitable hiring practices training for the Executive, Directors, and MES Groups:
 \item
  Build and run additional EDI training for the entire MES Council, at the discretion of the EDI Officer.
 \item
  Create an EDI library of pre-recorded training sessions for the MES and its constituents. These sessions are to be distributed upon request.
 \item
  Report to the President.
 \item
  Be a position held by a maximum of two people.
 \item
  Not hold any other position on the MES Council.

\end{enumerate}

\subsubsection{Fireball Coordinator(s)}
\label{fireball-coordinators}
The Fireball Coordinator(s) shall:

\begin{enumerate}
 \item
  Organize all aspects of the Fireball dinner, foremost:

  \begin{enumerate}
   \item
    Booking the reception hall
   \item
    Catering
   \item
    Selling tickets
   \item
    Decorations at dinner
   \item
    Arrange speakers list
  \end{enumerate}
 \item
  Work with the Awards Selection Committee to procure all Fireball award plaques once the recipients have been determined.
 \item
  Organize event ticket sales with the Drain Coordinator(s).
 \item
  Arrange for the Advertising Committee to promote sales and other campaigns.
 \item
  Report to the DoE.
 \item
  Be a position held by a maximum of three people.

\end{enumerate}

\subsubsection{Information Technology Coordinator(s)}
\label{information-technology-coordinators}
The Information Technology Coordinator(s) shall:

\begin{enumerate}
 \item
  Ensure the accessibility of all MES records, assisted by the Administrator and the Website Coordinator(s).
 \item
  Maintain the organization of information and streamline the UI interface of the MES website (macengsociety.ca) in coordination with the Website Coordinator(s) in accordance with the guidelines set out in MES Bylaws Section \ref{website}.
 \item
  Maintain the MES Google Workspace and the email service and mailing lists.
 \item
  Ensure the transition of Council, Appointed Positions, or other relevant parties onto MES electronic communication platforms. Including MES Microsoft Teams, and Google Workspace.
 \item
  Look after MES computer needs, including maintenance and installation of the machines in the MES Office.

  \begin{enumerate}
   \item
    The Information Technology Coordinator(s) must be consulted on the purchases of new hardware for the MES computers.
   \item
    The software on the MES computers is at the discretion of the Information Technology Coordinator(s) or any member of the MES Executive and should be used for official MES business only.
  \end{enumerate}
 \item
  Take appropriate action to protect passwords for the MES server, mailing lists, MES Office computer, and any other MES passwords.
 \item
  Develop protocols for the upkeep of MES technologies and technical platforms.
 \item
  Prepare an interim progress report and transition report (see Appendix J). % fix this lol
 \item
  Report to the VP Internal.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Wellness Coordinator(s)}
\label{wellness-coordinators}
The Wellness Coordinator(s) shall:

\begin{enumerate}
 \item
  Chair the Wellness Committee (see MES Bylaws Section \ref{wellness-committee}).
 \item
  Plan and execute events related to student wellness, education, and stress relief.
 \item
  Create social media initiatives to engage students.
 \item
  Report to the VPSL.
 \item
  Be a position held by a maximum of three people.

\end{enumerate}

\subsubsection{Kennedy Coordinator(s)}
\label{kennedy-coordinators}
The Kennedy Coordinator(s) shall:

\begin{enumerate}
 \item
  Organize all aspects of the Kennedy dinner, foremost:

  \begin{enumerate}
   \item
    Booking the reception hall
   \item
    Catering
   \item
    Selling tickets
   \item
    Decorations at dinner
   \item
    Arrange speakers list
   \item
    Invite appropriate faculty guests
  \end{enumerate}
 \item
  Coordinate with each program representative, program society, VPSL, DoE, Faculty, and University Health and Safety to plan, approve, and clean up all Kennedy pranks to ensure only safe and appropriate pranks are created.
 \item
  Report to the DoE.
 \item
  Be a position held by a maximum of three people.

\end{enumerate}
\subsubsection{macLAB Chair}
\label{maclab-chair}

The macLAB Chair shall:

\begin{enumerate}
 \item
  Advertise the benefits of the macLAB Fund, and administer the opt-out period on behalf of the MES, in accordance with macLAB Bylaws (see McMaster Laboratory Advancement Benefaction Endowment Fund Bylaws).
 \item
  Chair the macLAB board of directors
 \item
  Create plaques to be placed beside funded program projects.
 \item
  Report to the VPA.
 \item
  Be a position that must only be held by one person.

\end{enumerate}

\subsubsection{McMaster Engineering Competition Chair(s)}
\label{mcmaster-engineering-competition-chairs}
The McMaster Engineering Competition Chair(s) shall:

\begin{enumerate}
 \item
  Have prior experience with the MEC, either as a member of the MEC Committee or as a volunteer.
 \item
  Be ultimately responsible for MEC.
 \item
  Chair the MEC Committee (see MES Bylaws Section \ref{mcmaster-engineering-competition-committee}).
 \item
  Be responsible for recruiting/selecting members for the MEC Committee before the end of April alongside the VPA.
 \item
  Hold at least one MEC Committee meeting before the end of April.
 \item
  Ensure that MEC is held in advance of the Ontario Engineering Competition such that sufficient time is allowed for judging and registration of successful competitors for the Ontario Engineering Competition.
 \item
  Hold weekly MEC Committee meetings starting the second week of September.
 \item
  Liaise with Engineering Competition Chairs at other universities and the Ontario Engineering Competition Organizing Committee.
 \item
  Update the VPA on the MEC Committee's progress at least once per month and provide a progress report to the MES Executive in July, September, and November.
 \item
  Keep an official journal of progress for transitional purposes.
 \item
  Meet with winning teams to brief them and ensure professional representation at the Ontario Engineering Competition.
 \item
  Organize a post competition training workshop for the winning competitors.
 \item
  Work with the VPX to organize transportation, delegate fees, and all correspondence with the Ontario Engineering Competition and the Canadian Engineering Competition Organizing Committees for winning competitors of MEC attending the Ontario Engineering Competition and/or the Canadian Engineering Competition.
 \item
  Report to the VPA.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Trailer Coordinator(s)}
\label{trailer-coordinators}
The Trailer Coordinator(s) shall:

\begin{enumerate}
 \item
  Coordinate and record all MES rental activities and bookings for the MES Trailer.
 \item
  Complete a training course taught and evaluated by the previous Trailer Maintenance Coordinator(s).
 \item
  Be responsible for ensuring that groups using the MES Trailer are aware of how to safely operate it.
 \item
  Be responsible for the three sets of keys to the MES Trailer, and supply one set of keys to the VPF.
 \item
  Establish regular maintenance schedules and complete all necessary repairs efficiently and in a timely manner.
 \item
  Document all maintenance completed, related purchases, and complete proper paperwork for MES records.
 \item
  Enforce the MES Trailer policy (see MES Bylaws Section \ref{mes-trailer}) and report all violations to the MES Executive.
 \item
  Have the authority, on behalf of the Executive, to refuse use of the MES Trailer to a particular person or group.
 \item
  Be responsible for collecting fees on behalf of the MES should the trailer be used on any toll routes.
 \item
  Get the MES Trailer inspected and licensed annually in September.
 \item
  Ensure all clubs and teams renting the Trailer complete the appropriate forms and provide the appropriate deposits.
 \item
  Report to the VP Internal.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Plumbline Editor(s)}
\label{plumbline-editors}
The Plumbline Editor(s) shall:

\begin{enumerate}
 \item
  Produce a minimum of four issues of the Plumbline (see MES Bylaws Section \ref{plumbline}).
 \item
  Have an electronic copy of the Plumbline available for download on the MES website, on or prior to the day of hardcopy release.
 \item
  Report to the Publications Editor.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Frequency Editor(s)}
\label{frequency-editors}
The Frequency Editor(s) shall:

\begin{enumerate}
 \item
  Chair the Newsletter Committee (see MES Bylaws Section \ref{newsletter-committee}).
 \item
  Publish and distribute the Frequency quarterly to the McMaster Engineering undergraduate student body (see MES Bylaws Section \ref{frequency}).
 \item
  Actively seek contributions.
 \item
  Report to the Publications Editor.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Handbook Editor(s)}
\label{handbook-editors}
The Handbook Editor(s) shall:

\begin{enumerate}
 \item
  Be appointed in October to allow for a longer time to accumulate material for the Engineering Handbook.
 \item
  Compile the Engineering Handbook.
 \item
  Keep in mind that the primary targets for the Engineering Handbook are first year students.
 \item
  Keep the Engineering Handbook free of any discriminatory material.
 \item
  Use the Engineering Handbook to pass down McMaster Engineering traditions and information to first year students in a useful and humorous way (see MES Bylaws Section \ref{engineering-handbook}).
 \item
  List the annual MES awards in the Handbook along with a description of each award (see MES Bylaws Section \ref{mes-awards}).
 \item
  List a calendar of events, conferences, and competitions as supplied by the VPX and VPSL.
 \item
  List all of the involvement opportunities within McMaster Engineering.
 \item
  Report to the Publications Editor.
 \item
  Be a position held by a number of individuals decided at the discretion of the Publications Editor and VPC.

\end{enumerate}

\subsubsection{Publications Editor}
\label{publications-editor}
The Publications Editor shall:

\begin{enumerate}
 \item
  Oversee the organization, production, and editing of the following publications:

  \begin{enumerate}
   \item
    Frequency
   \item
    Plumbline
   \item
    Handbook
  \end{enumerate}
 \item
  Enforce the Editorial Policy for all MES publications (see MES Bylaws Section \ref{editorial-policy}).
 \item
  Chair the Editorial Review Committee to enforce and review Editorial Policy (see MES Bylaws Section \ref{editorial-review-committee}).
 \item
  Coordinate with the Website Coordinator(s) to maintain and update online publications.
 \item
  Prepare an interim progress report and transition report (see Appendix J). % fix this lol
 \item
  Ensure all publications are reviewed by the President and the Equity and Inclusion Officer prior to publishing.
 \item
  Work with the Sustainability Coordinator(s) to ensure sustainable practices in the printing of our publications.
 \item
  Sit on the Advertising Committee.
 \item
  Work with the Advertising Committee to actively search for more ways to promote MES productions to the McMaster Engineering student body.
 \item
  Report to the VPC.
 \item
  Supervises the following positions:

  \begin{enumerate}
   \item
    Handbook Editor(s)
   \item
    Frequency Editor(s)
   \item
    Plumbline Editor(s)
  \end{enumerate}
 \item
  Be a position held by a maximum of one person.

\end{enumerate}

\subsubsection{Professional Development Coordinator(s)}
\label{professional-development-coordinators}
The Professional Development Coordinator(s) shall:

\begin{enumerate}
 \item
  Chair the Professional Development Committee (see MES Bylaws Section \ref{professional-development-committee})
 \item
  Collaborate with the Professional Development Committee and the MES Executive to bring forward new professional development initiatives
 \item
  Organize event demographic and feedback collection.
 \item
  Report to the VPA.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Leadership Development Conference Coordinator(s)}
\label{leadership-development-conference-coordinators}
The Leadership Development Conference Coordinator(s) shall:

\begin{enumerate}
 \item
  Chair the Leadership Development Conference
 \item
  Collaborate with the Leadership Development Conference Organizing Committee, Professional Development Committee (?), and the MES Executive to bring forward a conference surrounding Leadership Development
 \item
  Organize event demographic and feedback collection.
 \item
  Report to the VPX
 \item
  Be a position held by a maximum of two people.
\end{enumerate}

\subsubsection{Administrator}
\label{administrator}
The Administrator shall:

\begin{enumerate}
 \item
  Be the custodian of all MES records, assisted by the IT Coordinator(s).
 \item
  Within one month of the start of each term, schedule and advertise:

  \begin{enumerate}
   \item
    MES Council meeting dates and times
   \item
    MES Executive office hours' dates and times
  \end{enumerate}
 \item
  Collect event dates and details from Team members and update the MES calendar. All calendar events should have the following:

  \begin{enumerate}
   \item
    Name
   \item
    Event description
   \item
    Event location
   \item
    Relevant sign-up and advertising links
   \item
    Relevant contact person with their contact information
  \end{enumerate}
 \item
  Collect and distribute all internal MES correspondence
 \item
  Take and distribute the minutes and agendas of all MES Council and General Meetings. Council minutes shall be made available for review and continuity in a public forum within a week after the meeting has occurred
 \item
  Forward motions for funding to the VPF as they are received
 \item
  Be responsible for sending out MES Council meeting agendas ahead of each MES Council and General Meeting
 \item
  Be responsible for ensuring the public accessibility MES Council meeting minutes on the MES website within one week of the meeting.
 \item
  Record attendance at MES Council meetings and enforce the Attendance Policy (see MES Bylaws Section \ref{attendance}).
 \item
  Maintain the MES Office, including the purchasing of resources such as stationary, letterhead, business cards, and other office supplies (see MES Bylaws Section \ref{office-equipment}).
 \item
  Report to the VP Internal.
 \item
  Be a position held by a maximum of one person.

\end{enumerate}

\subsubsection{Graphic Designer(s)}
\label{graphic-designers}
The Graphic Designer(s) shall:

\begin{enumerate}
 \item
  Design graphics for various platforms and mediums for each MES advertising campaign as requested.
 \item
  Complete other design projects as requested by the MES Executive.
 \item
  Be knowledgeable about advertising, graphic design, and the requirements for common advertising avenues (ie. MSU poster guidelines, JHE Lobby TVs, Hatch TVs, Charging Station, file types and formats)
 \item
  Ensure that designs are created in a timely manner.
 \item
  Be responsible for creating a design to the client's specification
 \item
  Develop and encourage new initiatives to increase exposure and effectiveness of advertising techniques
 \item
  Create promotional videos for advertisement campaigns as requested by the MES Executive.
 \item
  Report to the VPC.
 \item
  Be a position held by a number of individuals decided at the discretion of VPC.

\end{enumerate}

\subsubsection{External Conference or Competition Chair(s)}
\label{external-conference-or-competition-chairs}
Conference or Competition Chair(s) are to be established as seen fit by
the MES Executive to run an Engineering Students Societies' Council of
Ontario (ESSCO) or Canadian Federation of Engineering Students (CFES)
event. If there are multiple conferences or competitions being planned
at McMaster at the same time, all chairs shall hold appointed positions
on the MES.

The Conference or Competition Chair(s) shall:

\begin{enumerate}
 \item
  Be in charge of organizing an ESSCO or CFES conference or competition at McMaster, after successfully winning a bid.
 \item
  Be ratified at the General Meeting immediately following their successful bid.
 \item
  Give a final presentation at the General Meeting immediately following the conclusion of the conference or competition.

  \begin{enumerate}
   \item
    Upon completion of this presentation, the chair(s) will have completed their term as an appointed position on the MES.
  \end{enumerate}
 \item
  Report to the VPX.

\end{enumerate}

\subsubsection{Sports Coordinator(s)}
\label{sports-coordinators}
The Sport Coordinator(s) shall:

\begin{enumerate}
 \item
  Organize team sports events both internal and externally to the MES.
 \item
  Chair the Sports Committee (see MES Bylaws Section \ref{sports-committee}).
 \item
  Encourage participation in intramurals and program team competitions.
 \item
  Maintain contact, through the VPX, with other engineering schools to coordinate inter-school challenges.
 \item
  Publicize all relevant sporting tournaments in MES publications.
 \item
  Prepare an events schedule at the beginning of their term to be published in the Engineering Handbook.
 \item
  Initiate at least one new activity; such as a weekend trip, a hosted tournament, or a homecoming activity.
 \item
  Coordinate support and involvement in MES-sponsored sports teams with the VPSL.
 \item
  Organize the annual Ratboy Memorial Soccer Tournament and initiate/coordinate other intrafaculty sports tournaments.
 \item
  Organize and maintain the collection of sports equipment rentals in the MES office.
 \item
 Promote the Intramural Funding applications, in collaboration with the VP Finance.
 \item
  Report to the DoE.
 \item
  Be a position held by a maximum of three people.
\end{enumerate}

\subsubsection{Gerald Hatch Centre Student Coordinator(s)}
\label{gerald-hatch-centre-student-coordinators}
The Gerald Hatch Centre Student Coordinator(s) shall:

\begin{enumerate}
 \item
  Act as a liaison between the MES and the McMaster Faculty of Engineering for issues relating to the Gerald Hatch Centre.
 \item
  Serve on the Hatch Operations Committee (Faculty Committee).
 \item
  Be responsible for the Hatch Booking System.
 \item
  Work with VPI and DoC to organize meeting times and space allocations for MES Clubs and Teams in the Gerald Hatch Centre.
 \item
  Allocate Gerald Hatch Centre 2nd floor lockers to Capstone Project groups.
 \item
  Be responsible for organizing renovations and improvements to the Gerald Hatch Centre, including those to the Drain or the DW Lounge.
 \item
  Be responsible for troubleshooting the Via Kramer system in the Hatch 2nd floor Meeting Rooms.
 \item
  Be responsible for troubleshooting and ensuring functionality of the Hatch TVs.
 \item
  Update the Hatch Procedural Manual, when needed.
 \item
  Report to the VP Internal.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Mentorship Coordinator(s)}
\label{mentorship-coordinators}
The Mentorship Program Coordinator(s) shall:

\begin{enumerate}
 \item
  Recruit upper year students into the MES Mentorship Program as mentors.
 \item
  Advertise the MES Mentorship Program to incoming first year students as a potential resource.
 \item
  Maintain a database of all current mentors and mentees involved in the MES Mentorship Program.
 \item
  Match up incoming mentees to mentors before the end of September.
 \item
  Plan applicable monthly themes for the MES Mentorship Program to assist mentors in reaching out to their mentees.
 \item
  Organize at least three events throughout the year, one of which should be during Back2School Week as a kickoff event.
 \item
  Be the main point of contact for all mentors volunteering for the MES Mentorship Program.
 \item
  Reach out to alternative mentorship programs running under the Faculty of Engineering to develop ties between the programs.
 \item
  Report to the VPA.
 \item
  Be a position held by a maximum of three people.

\end{enumerate}

\subsubsection{Sustainability Coordinator(s)}
\label{sustainability-coordinators}
The Sustainability Coordinator(s) shall:

\begin{enumerate}
 \item
  Oversee the sustainability section of the University Health and Safety submission form. This both involves updating the questions and resources attached as needed, as well as providing feedback to groups who submit forms on how they can make their events more sustainable.
 \item
  Work with the DoE to improve the sustainability of MES events.
 \item
  Evaluate what resources the MES can provide to make events more sustainable, and work to provide to improve the sustainability of subsidiaries' events and operations.
 \item
  Work with the Rental Coordinator(s) to ensure that subsidiaries are aware of available sustainability related resources such as the water jugs, kettle, etc.
 \item
  Organize a battery collection drive and electronics collection drive at least once a year.
 \item
  Chair the Sustainability Committee (see MES Bylaws Section \ref{sustainability-committee}).
 \item
  Carry out the goals and support the events and ideas brought forward by the Sustainability Committee.
 \item
  Work with other MES members, including appointed positions, to run regular MES programming and operations in a more sustainable manner.
 \item
  Actively search for ways that the MES can improve its sustainability.
 \item
  Report to the Vice President, Internal.
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Social Media Coordinator(s)}
\label{social-media-coordinators}
The Social Media Coordinator(s) shall:

\begin{enumerate}
 \item
  Coordinate all social media posts promoting MES initiatives. These platforms include but are not limited to Facebook, Instagram, Snapchat, Twitter, TikTok, and LinkedIn.
 \item
  Promote Program and External Opportunities on social media platforms as appropriate.
 \item
  Update the MES website with new content including, but not limited to, the Events Calendar, Home Page Themes, and Special Webpages.
 \item
  Actively search for new ways that the MES can reach a broader audience.
 \item
  Coordinate with the Administrator to make meeting minutes available to the public.
 \item
  Lead the National Engineering Month campaign with VPX.
 \item
  Report to the VPC.
 \item
  Be a position held by a number of individuals decided at the discretion of VPC..

\end{enumerate}

\subsubsection{Content Coordinator(s)}
\label{content-coordinators}
The Content Coordinator(s) shall:

\begin{enumerate}
 \item Produce videos to promote MES ongoings.
 \item Ensure that all videos are relevant to the MacEng student body and reflect the MES in a positive light.
 \item Work with the Social Media Coordinator(s) to cross-post videos on TikTok and Instagram.
\end{enumerate}

\subsubsection{Student Projects Coordinator(s)}
\label{special-projects-coordinators}

The Student Projects Coordinator(s) shall:
\begin{enumerate}
 \item
  Maintain the integrity of the Special Projects Fund, and strive to fulfill its intended purpose.
 \item
  Create and implement methods of receiving applications, tracking the progress of all current projects, and showcasing all current and past projects
 \item
  Approve Special Projects funding applications for less than \$500, once a majority vote from the VPSL, the VPF, and the President is reached.
 \item
  Coordinate with the VPF to ensure Special Projects funding recipients receive reimbursements.
 \item
  Coordinate with the Frequency Editor's to have articles published in the Frequency for all projects greater than \$1000.
 \item
  Report to the President
 \item
  Be a position held by a maximum of two people.

\end{enumerate}

\subsubsection{Sponsorship Coordinator(s)}
\label{sponsorship-coordinators}
The Sponsorship Coordinator(s) shall:

\begin{enumerate}
 \item
  Work with the VPF to budget for expected sponsorship revenue throughout the upcoming year.
 \item
  Work with the Advertising Committee to maintain an up-to-date sponsorship package.
 \item
  Reach out to grassroots businesses regarding sponsorship opportunities for the MEScard.
 \item
  Act as the primary point of contact for any MES sponsors throughout the sponsorship relationship.
 \item
  Maintain a database of long-term sponsors of the MES.
 \item
  Maintain relationships with long-term sponsors of the MES.
 \item
  Assist MES Clubs and Teams' sponsorship organizers in maintaining and acquiring sponsorship and corporate relationships.
 \item
  Report to the VPC.
 \item
  Be a position held by a maximum of two people.
\end{enumerate}

\subsection{Transition}
\label{transition}
\subsubsection{Objectives}
\label{objectives}
The objectives of transition are to:

\begin{enumerate}
 \item
  Effectively transfer the duties, goals and initiatives from outgoing to incoming MES Team members and ensure continuity within the MES.
 \item
  Establish both short and long term mandates for individual MES Team positions and for the MES to promote momentum for traditional activities and new opportunities.
 \item
  Generate spirit and enthusiasm for incoming MES Team members to maintain or enhance current MES standards and traditions.
 \item
  Provide some professional development activities for MES Team members.
 \item
  Give MES Team members a chance to interact on both a professional and a social level.

\end{enumerate}

\subsubsection{Transition Reports}
\label{transition-reports}
Transition reports for each elected and appointed position are stored on
the Google Drives of the MES Executive as well as the position holder.
The reports shall be updated informally throughout the year by the
position holders to include any challenges or new initiatives for the
position. The reports will also be formally updated at the end of
January by the MES Executive through the transition interview as
described in the MES Bylaws Section \ref{team-transition-process}. % fix this lol - idk what this should be referring to

\subsubsection{Team Transition Process}
\label{team-transition-process}

The transition process consists of the following:

\begin{enumerate}
 \item
  General Transition Protocol:

  \begin{enumerate}
   \item
    The transition process shall be overseen by the Chief Returning Officer and the outgoing President.
   \item
    The Chief Returning Officer shall ensure that there is at least a one week break between all positions' exit interviews and the start of the general elections.
   \item
    The Chief Returning Officer shall ensure that there is at least a two week break between the end of general elections and SAGM II to ensure sufficient time for transition meetings.
  \end{enumerate}
 \item
  Exit Interviews

  \begin{enumerate}
   \item
    All elected and appointed positions shall receive an interview with the Chief Returning Officer, the outgoing President, and the incoming President.
   \item
    Interviews will be conducted prior to the ratification of the incoming Council at the winter general meeting.
   \item
    The interviews will be conducted to update the transition documents as well as determine any changes to the responsibilities of the position, new challenges faced by the position or any initiatives started by the holder of the position.
   \item
    Information collected from these interviews shall be used to update the advertisements and descriptions of each position, if applicable.
  \end{enumerate}
 \item
  Transition Meetings

  \begin{enumerate}
   \item
    An MES Council meeting consisting of the current MES Council as well as their elected successors shall be held between the end of elections and SAGM 2.
   \item
    The purpose of this meeting will be to introduce the incoming MES Council members to the structure of MES meetings, and to give them an opportunity to meet and go over their transition documents with their predecessors. If either the outgoing or incoming member is unable to attend this meeting, it is the responsibility of the outgoing member to arrange a meeting with the incoming member, to go over the transition documents.
  \end{enumerate}
 \item
  Transition Social

  \begin{enumerate}
   \item
    A social event shall be planned by the outgoing VPSL for the days following the Transition Meeting.
   \item
    All members of the outgoing and the incoming MES Team shall be invited.
   \item
    This shall serve as an informal setting in which the new MES Team can ask more questions of their predecessors and meet other members of the incoming MES Team.
  \end{enumerate}
\end{enumerate}

\subsection{Appointed Positions}
\label{appointed-positions-selection}

\subsubsection{Appointment Procedure}
\label{appointment-procedure}
\begin{enumerate}
 \item
  All interested candidates must complete an online application form once it is available by a deadline set at the discretion of the MES Executive.
 \item
  The MES Executive, Directors, and in some cases, the MES Team member currently holding the position sought, will review the applications, and applicants will be contacted for interviews during the following week. Interviews and selections will be conducted by the MES Executive and in some cases, the Directors and the outgoing position holder.
 \item
  Candidates are not required to hold an MES membership before applying for an appointed position. However, appointed positions are required to hold an MES membership for the primary academic year in which they hold the position.

  \begin{enumerate}
   \item
    Individuals may hold an appointed position on the MES without holding an MES membership throughout their term. This exception shall be granted on a financial need basis at the discretion of the Chief Returning Officer.
  \end{enumerate}

\end{enumerate}

\subsubsection{Regular Appointed Positions}
\label{regular-appointed-positions}
The following positions will be appointed after the general elections
using the appointment procedure (see MES Bylaws Section \ref{appointment-procedure}): % useless reference to the procedure immediately preceding this list

\begin{enumerate}
 \item
  Administrator
 \item
  Bus Monitor Lead
 \item
  Chief Returning Officer
 \item
  Culture Coordinator(s)
 \item
  Drain Coordinator(s)
 \item
  DW Lounge Coordinator(s)
 \item
  Equity and Inclusion Officer
 \item
  Fireball Coordinator(s)
 \item
  First Year Council Coordinator
 \item
  Frequency Editor(s)
 \item
  Gerald Hatch Centre Student Coordinator(s)
 \item
  Graphic Designer(s)
 \item
  Information Technology Coordinator(s)
 \item
  Kennedy Coordinator(s)
 \item
  Professional Development Coordinator(s)
 \item
  Leadership Development Committee Coordinator(s)
 \item
  macLAB Chair
 \item
  Mentorship Coordinator(s)
 \item 
  MESSCO Coordinator(s)
 \item
  Plumbline Editor(s)
 \item
  Publications Editor
 \item
  Social Media Coordinator(s)
 \item
  Student Projects Coordinator(s)
 \item
  Sponsorship Coordinator(s)
 \item
  Sports Coordinator(s)
 \item
  Sustainability Coordinator(s)
 \item
  Trailer Coordinator(s)
 \item
  Website Coordinator(s)
 \item
  Wellness Coordinator(s)
 \item
  Photographer/Videographer(s)
\end{enumerate}

\subsubsection{Co-Orientation Coordinators}
\label{co-orientation-coordinators-eligibility}
The following is the procedure for selecting the Co-Orientation
Coordinators:

\begin{enumerate}
 \item
  Eligibility

  \begin{enumerate}
   \item
    Co-OCs must apply in pairs.
   \item
    Co-OCs pairs must both be registered in level 3 or above.
   \item
    Both of the Co-OCs must have served for at least one year as a Welcome Week Representative.

    \begin{enumerate}
     \item
      During the selection phase, preference will be given to pairs where at least one of the Co-OCs must have served for at least one year on the WW Orientation Committee.
    \end{enumerate}
   \item
    Must be and maintain full MES member status until completion of term
  \end{enumerate}
 \item
  Meeting Procedure:

  \begin{enumerate}
   \item
    Applicant pairs should have up to 15 minutes of uninterrupted presentation time to present to council.
   \item
    Applicant pairs should have up to 25 minutes of question period following applicant presentations.
   \item
    Following all applicants' presentations and questions there should be 20 minutes of general discussion of the applicant pairs without the applicant pairs present in the room.
  \end{enumerate}
 \item
  Selection

  \begin{enumerate}
   \item
    Voting shall be done by the MES President, the Faculty of Engineering Associate Dean, Undergraduate Studies, the Faculty of Engineering Assistant Dean, Undergraduate Studies, and the outgoing Co-OCs.
   \item
    Successful candidates should require a simple majority of votes cast.
   \item
    All voting members must be present to have a valid vote.
   \item
    The MES President is to inform the selected candidates of their selection.
  \end{enumerate}

\end{enumerate}

\subsubsection{Chief Returning Officer}
\label{chief-returning-officer-eligibility}
\begin{enumerate}
 \item
  The position may be referred to as Council Chair, Chair, or Speaker if the need to distinguish those distinct responsibilities of the portfolio arise.
 \item
  In the case that the Chief Returning Officer successfully campaigns and is elected in the Bachelor of Technology Rep or Presidential elections, they must resign from their position as Chief Returning Officer, and a new Chief Returning Officer be appointed for the remainder of the term.
 \item
  In the case that the Chief Returning Officer campaigns and is elected during General Elections, they may continue in their duties as Chief Returning Officer for the remainder of the term, such that::

  \begin{enumerate}
   \item
    the Chief Returning Officer may still chair the second term General Meeting.
   \item
    the Chief Returning Officer may no longer chair MES Council meetings by default. Following the bylaws as stated in MES Bylaws Section \ref{meetings-general}.\ref{CRO-chair-meetings}, the president will chair any MES Council meetings, unless the President declines or is unable to chair. A vote will then be held to elect a new chair, where the Chief Returning Officer may be elected as chair. The Chief Returning Officer may still hold their voting power from their elected position. % fix this lol - need to fix this reference
  \end{enumerate}
\end{enumerate}

\subsubsection{Other Appointed Positions}
\label{other-appointed-positions}
The following positions will be appointed at their respective times
throughout the year using the appointment procedure (see MES Bylaws
Section \ref{appointment-procedure}):

\begin{enumerate}
 \item
  The Handbook Editor(s) shall be appointed before the end of November.
 \item
  External Competition or Conference Chair(s) shall be appointed upon a successful bid.
 \item
  The MEC Chair(s) shall be appointed before the end of November.
\end{enumerate}
% \end{document}
