\section{Committees}
\label{committees}

\subsection{General}
\label{committees-general}
Committees shall operate by majority vote procedure. The Chair shall
have no voting rights at the meeting except in the case of a tie. The
Chair has the deciding vote in the case of a tie.

\subsubsection{Responsibilities of the Chair}
\label{responsibilities-of-the-chair}

\begin{enumerate}
 \item
  The Chair will conduct all meetings of their committee to ensure each member has time to share their views and ideas with other members of the committee.
 \item
  The Chair shall ensure that the meetings will maintain a sense of open friendliness, and correct the behaviour of certain members should they be promoting ill will, or feelings of discomfort, towards other members of the committee.
 \item
  The Chair has the right to discuss removal of a committee member with the President should they decide the committee cannot function properly with this member present. The President will decide whether removal seems necessary, and instruct the Chairperson accordingly.
\end{enumerate}

\subsubsection{Membership}
\label{membership}
\begin{enumerate}
 \item
  The Chairs and Council membership for each Standing Committee shall be ratified, and made public, by the second MES meeting following the start of each school year.
 \item
  The Chair is responsible to recruit members for their committee from the general membership of the MES.

\end{enumerate}

\subsection{Welcome Week Orientation Planning Committee}
\label{welcome-week-orientation-planning-committee}
\begin{enumerate}
 \item
  The Co-Orientation Coordinators shall select the members of the Welcome Week Orientation Planning Committee, using an application process and interviewing if necessary.
 \item
  The Welcome Week Orientation Planning Committee members must have served as an engineering Welcome Week Representative for at least one year, as well as be familiar both with the MES and with the Engineering Welcome Week,
 \item
  Candidates are not required to hold an MES membership before applying for a position, however; individuals must become MES members once selected for this role.

  \begin{enumerate}
   \item
    Individuals may hold a position on the Welcome Week Orientation Planning Committee without holding an MES membership. This exception shall be granted on a financial need basis at the discretion of the Chief Returning Officer.
  \end{enumerate}
 \item
  The purpose of the Welcome Week Orientation Planning Committee is to help the Co-OCs with selecting Welcome Week Representatives and organizing Welcome Week.
 \item
  The Welcome Week Orientation Planning Committee may continue to assist the transition of first year students throughout the year.
 \item
  The Co-OCs and the Welcome Week Orientation Planning Committee are responsible for organizing all events related to Welcome Week including:

  \begin{enumerate}
   \item
    Summer communication to Welcome Week Reps indicating details of the summer bonding activity (Catapult), a schedule for Welcome Week and any other relevant information.
   \item
    Summer mailing to first year students indicating schedule and description of Welcome Week, MES first year flyer, and other relevant information.
   \item
    All events to take place during Welcome Week.
  \end{enumerate}
 \item
  The Welcome Week Orientation Committee will ensure that all activities, as well as the behaviour of the Welcome Week Reps, fall within the Welcome Week Values and Guiding Principles and the guidelines of the Student Success Centre.
 \item
  The Welcome Week Orientation Committee will prepare a budget for Welcome Week activities to be presented at the first council meeting before the summer.
 \item
  The President and the Faculty of Engineering's Assistant Dean, Undergraduate Studies, shall approve the final list of Welcome Week Representatives after the selection process and the final list of Welcome Week Representative names after the naming process.

\end{enumerate}

\subsection{Ad Hoc Committees}
\label{ad-hoc-committees}
\begin{enumerate}
 \item
  Ad Hoc Committees will be established as seen fit by the MES Executive, for the purposes of accomplishing short-term goals of the MES.
 \item
  The MES Executive shall appoint Chairs for Ad Hoc Committees.
 \item
  The MES Executive will determine the purpose of these Committees in conjunction with the approved Chair for the Committee.
 \item
  The MES Executive will determine the duration of an Ad Hoc Committee's existence in conjunction with the Chair of that Committee.

\end{enumerate}

\subsection{Standing Committees}
\label{standing-committees}
Standing Committees shall hold meetings at least once a term for the
entire academic year. The Chair may call as many additional meetings
each month as they deems necessary.

\subsubsection{Advertising Committee}
\label{advertising-committee}

\begin{enumerate}
 \item
  The VPC shall chair the Advertising Committee.
 \item
  The Advertising Committee is responsible for ensuring advertising campaigns are made for each event coordinated by an event coordinator, MES Executive, or Director, and sponsored by the MES.
 \item
  Promote external campaigns on MES Social Media platforms where appropriate, including but not restricted to sharing program events, external opportunities, and ECCS initiatives.
 \item
  The members of the Advertising Committee shall consist of:

  \begin{enumerate}
   \item
    Graphic Designers
   \item
    Social Media Coordinator(s)
   \item
    Website Coordinator(s)
   \item
    Publications Editor
   \item
    Photographer/Videographer(s)
  \end{enumerate}
 \item
  The Committee is responsible for that media content (such as flyers, posters, posts, stories, and videos) are created, in coordination with the brand, for all MES events.

\end{enumerate}

\subsubsection{Awards Selection Committee}
\label{awards-selection-committee}
\begin{enumerate}
 \item
  The Chief Returning Officer shall chair the committee. The Chair is responsible for finding a Faculty member and a student to sit on the Committee.
 \item
  The members of the Awards Selection Committee shall consist of:

  \begin{enumerate}
   \item
    Administrator
   \item
    Vice President, Student Life
   \item
    One Faculty member
   \item
    One student who is not a MES Council member
  \end{enumerate}
 \item
  The Awards Selection Committee is responsible for administering procedures for the following awards:

  \begin{enumerate}
   \item
    ``Image of an Engineer'' Awards
   \item
    Faculty Appreciation Award
   \item
    Outstanding Teaching Assistant Award
  \end{enumerate}
 \item
  The Awards Selection Committee will investigate and publicize other potential award programs open to undergraduate engineering students.

\end{enumerate}

\subsubsection{Club Leaders Committee}
\label{club-leaders-committee}
\begin{enumerate}
 \item
  The DoC shall chair the Club Leaders Committee.
 \item
  The members of the Club Leaders committee shall consist of:

  \begin{enumerate}
   \item
    Vice President, Student Life
   \item
    Program Representatives
   \item
    First Year Representatives
   \item
    Club Presidents
   \item
    Director of Clubs
  \end{enumerate}
\end{enumerate}

The purpose of the Club Leaders Committee is to discuss relevant issues, coordinate club funding with the help of the DoC, and facilitate interaction between clubs.

\subsubsection{Delegate Selection Committee}
\label{delegate-selection-committee}

\begin{enumerate}
 \item
  The VPX shall chair the Delegate Selection Committee.
 \item
  The Delegate Selection Committee shall accept applications from McMaster undergraduate engineering students interested in becoming a delegate on behalf of the MES at closed conferences.
 \item
  The members of the Delegate Selection Committee shall be a minimum of 3 individuals consisting of:

  \begin{enumerate}
   \item
    Vice President, External Relations
   \item
    The remainder of the committee shall be composed of other faculty of engineering students not attending the conference, as selected by the VPX
  \end{enumerate}
 \item
  The Delegate Selection Committee should remain uniform when selecting delegates unless a conflict arises from the membership indicated in c), above.
\end{enumerate}

\subsubsection{Editorial Review Committee}
\label{editorial-review-committee}
\begin{enumerate}
 \item
  The Publications Editor shall chair the Editorial Review Committee.
 \item
  The Editorial Review Committee must review and unanimously approve of all material being considered for all MES publications in accordance with the editorial policies of the MES (see ``Services'', Section F.1.3).
 \item
  The members of the Editorial Review Committee shall consist of:

  \begin{enumerate}
   \item
    Vice President, Communications
   \item
    Editors of the Plumbline, Frequency and Handbook.
   \item
    Equity and Inclusion Officer.
   \item
    A member of the MES Executive.
   \item
    Two McMaster undergraduate students in the Faculty of Engineering.
  \end{enumerate}
 \item
  The Editorial Review Committee shall assist the Publications Editor with their responsibilities.
 \item
  The Editorial Review Committee shall be responsible for the distribution of MES productions.

\end{enumerate}

\subsubsection{Elections Committee}
\label{elections-committee}
\begin{enumerate}
 \item
  The Chief Returning Officer shall chair the Elections Committee.
 \item
  The voting members of the Elections Committee shall consist of:

  \begin{enumerate}
   \item
    President
   \item
    Vice President, Student Life
   \item
    Equity and Inclusion Officer
  \end{enumerate}
 \item
  The Elections Committee shall fulfill their responsibilities as set out in the MES Bylaws Section C.1.7.

\end{enumerate}

\subsubsection{macLAB Board of Directors}
\label{maclab-board-of-directors}
See the McMaster Laboratory Advancement Benefaction Endowment Fund
By-Laws document for details.

\subsubsection{First Year Committee}
\label{first-year-committee}

\begin{enumerate}
 \item
  The VPSL shall chair the First Year Committee
 \item
  The members of the First Year Committee shall consist of:

  \begin{enumerate}
   \item
    Six First Year Representatives (see MES Bylaws Section B.4.3)
  \end{enumerate}
 \item
  The purpose of the First Year Committee is to coordinate activities and fundraising initiatives for the first year class.
\end{enumerate}

\subsubsection{Kennedy Committee}
\label{kennedy-committee}
\begin{enumerate}
 \item
  The Kennedy Coordinator(s) shall chair the Kennedy Committee.
 \item
  The members of the Kennedy Committee shall consist of:

  \begin{enumerate}
   \item
    Director of Events
   \item
    Vice President, Student Life
  \end{enumerate}
 \item
  The Kennedy Committee is responsible for organizing the Kennedy Dinner to follow the Iron Ring Ceremony.
 \item
  The Kennedy Committee shall establish a "Clean-up" Committee for the purpose of showing good faith to the University by helping to clean up unapproved Kennedy ``pranks'' known to occur the night before the Iron Ring Ceremony.

\end{enumerate}

\subsubsection{Newsletter Committee}
\label{newsletter-committee}
\begin{enumerate}
 \item
  The Frequency Editor(s) shall chair the Newsletter Committee.
 \item
  The members of the Newsletter Committee shall consist of:

  \begin{enumerate}
   \item
    Sports Coordinator(s)
   \item
    Administrator
   \item
    Vice President,Student Life
   \item
    Director of Events
   \item
    Program Representatives
   \item
    Information Technology Coordinator(s)
   \item
    Any other undergraduate engineering students
  \end{enumerate}
 \item
  The Newsletter Committee's purpose is to provide relevant articles for the production of the Frequency to keep engineering students up to date and informed on MES activities.

\end{enumerate}

\subsubsection{Student Life Committee}
\label{student-life-committee}
\begin{enumerate}
 \item
  The Vice President, Student Life and DoE shall chair the Student Life Committee,
 \item
  The members of the Student Life Committee shall consist of:

  \begin{enumerate}
   \item
    Fireball Coordinator(s) and Fireball Committee
   \item
    Kennedy Coordinator(s) and Kennedy Committee
   \item
    Wellness Coordinator(s) and Wellness Committee
   \item
    Sports Coordinator(s) and Sports Committee
   \item
    Sustainability Coordinator(s) and Sustainability Committee
   \item
    Culture Chair(s) and Culture Committee
   \item
    Outgoing Director of Events
   \item
    Any other undergraduate engineering students
  \end{enumerate}
 \item
  The remainder of the Student Life Committee shall be composed of a variety of Faculty of Engineering students from different years and disciplines.
 \item
  Any Student Life Committee member who volunteers for a particular event shall receive a discounted or free ticket to the event at the discretion of the Director of Events.
 \item
  The Student Life Committee shall be responsible for the coordination of the following specific events:

  \begin{enumerate}
   \item
    Engineering Pubs
   \item
    Fireball
   \item
    Kennedy

  \end{enumerate}
 \item
  The Student Life Committee shall act as a shared volunteer base between the committees of the Student Life portfolio.
\end{enumerate}

\subsubsection{Sports Committee}
\label{sports-committee}
\begin{enumerate}
 \item
  The Sports Coordinator(s) shall chair the Sports Committee.
 \item
  The members of the sports committee shall consist of:

  \begin{enumerate}
   \item
    Director of Events
   \item
    Vice President, Student Life
   \item
    Program Representatives
   \item
    First Year Representatives
  \end{enumerate}
 \item
  The Sports Committee is responsible for organizing intramural sporting activities.
 \item
  The Sports Committee shall organize any special sporting events which would be of interest to the MES such as:

  \begin{enumerate}
   \item
    Intrafaculty challenges
   \item
    Interfaculty challenges
   \item
    Ratboy Memorial Soccer Tournament
   \item
    Dodgeball Tournament

  \end{enumerate}
\end{enumerate}

\subsubsection{McMaster Engineering Competition Committee}
\label{mcmaster-engineering-competition-committee}
\begin{enumerate}
 \item
  The MEC Chair(s) shall chair and select the members of the MEC Committee.
 \item
  The Committee is responsible for ensuring the success of MEC as a qualifying event for OEC.
 \item
  The structure of the Committee shall be determined by the MEC Chair(s) and is to be approved by the VP Academic.

\end{enumerate}

\subsubsection{Culture Committee}
\label{culture-committee}
\begin{enumerate}
 \item
  The Culture Chair(s) shall chair the Culture Committee.
 \item
  Any other undergraduate engineering student can serve on this committee.
 \item
  The Culture Committee is responsible for assisting the Culture Chair in the running of Santa Hog, the Santa Claus Parade, Pi Day, and any other events organized by the Culture Chair.
 \item
  The Culture Committee shall assist in the gathering and recording of information regarding tradition including but not limited to:

  \begin{enumerate}
   \item
    Songs/Cheers
   \item
    Redsuit / MES position information
   \item
    Contact information with past engineering graduates
   \item
    Stories from iii)

  \end{enumerate}
\end{enumerate}

\subsubsection{Professional Development Committee}
\label{professional-development-committee}
\begin{enumerate}
 \item
  The Professional Development Coordinator(s) shall chair the Professional Development Committee.
 \item
  The Committee is responsible for assisting in the running of events such as:

  \begin{enumerate}
   \item
    LinkedIn photoshoots
   \item
    Professional development workshops
   \item
    Technical tutorials
   \item
    Any other initiatives from the Professional Development Committee Chair(s)
  \end{enumerate}
\end{enumerate}

\subsubsection{Leadership Development Conference Committee}
\label{leadership-development-conference-committee}
\begin{enumerate}
 \item
  The Leadership Development Conference Coordinator(s) shall chair the Leadership Development Conference Committee
 \item
  The Committee is responsible for assisting in the running of the conference with positions such as:

  \begin{enumerate}
   \item
    VP Marketing
   \item
    VP Logistics
   \item
    VP Seminars
   \item
    Any other positions as deemed necessary by the Leadership Development Conference Coordinator(s)

  \end{enumerate}
\end{enumerate}

\subsubsection{Wellness Committee}
\label{wellness-committee}
\begin{enumerate}
 \item
  The Wellness Coordinator(s) shall chair and select the members of the Wellness Committee.
 \item
  The Wellness Committee is responsible for ensuring an appropriate amount of events related to student wellness, education, and stress relief are run each term.
 \item
  The structure of the Wellness Committee shall be determined by the Wellness Coordinator(s) and is to be approved by the VPSL

\end{enumerate}

\subsubsection{Sustainability Committee}
\label{sustainability-committee}
\begin{enumerate}
 \item
  The Sustainability Coordinator(s) shall chair and select the members of the Sustainability Committee.
  \begin{enumerate}
   \item The Vice-President Student Life will be an ex-officio member of the committee.
  \end{enumerate}
 \item
  The Sustainability Committee is responsible for ensuring an appropriate amount of events related to sustainability and leadership in sustainability are run each term.
 \item
  The Sustainability Committee shall seek ways that students can engage with the McMaster Community on sustainability, and ways in which engineering students can support sustainability efforts on and off campus.
\end{enumerate}

\subsubsection{Academic Services Committee}
\label{academic-services-committee}
\begin{enumerate}
 \item
  The DoAR shall chair the Academic Services Committee.
 \item
  The Academic Services Committee will be composed of upper year student `course leads' chosen by the DoAR:

  \begin{enumerate}
   \item
    Course leads will be assigned by the DoAR to run sessions on a case by case basis.
   \item
    Course leads will be responsible for supplying the DoAR with a review/study plan before running a session.
   \item
    Course leads will be expected to show up to their assigned session and deliver a review session on the respective material for the course.
   \item
    Course leads will be paid for the hours spent running the sessions at a rate higher than the minimum wage and determined by the DoAR.
  \end{enumerate}
 \item
  The Academic Services Committee is responsible for assisting in running MES Help Sessions throughout the year, as well as assisting the DoAR with administrative responsibilities where appropriate.

\end{enumerate}

\subsubsection{Bus Monitor Committee}
\label{bus-monitor-committee}
\begin{enumerate}
 \item
  The Bus Monitor Lead shall chair the Bus Monitor Committee.
 \item
  The Bus Monitor Committee shall consist of the following members:

  \begin{enumerate}
   \item
    Bus Monitor Lead
   \item
    Director of Events
   \item
    VP Student Life
   \item
    All volunteer bus monitors
  \end{enumerate}
 \item
  Any Bus Monitor Committee member who volunteers as a bus monitor for a particular event shall receive a discounted or free ticket into the event at the discretion of the DoE.\hspace{0pt} \hspace{0pt}Tickets for Kennedy Formal and Fireball will be available at a reduced cost for bus monitors (at the discretion of the respective coordinator(s)).
 \item
  Online and in-person training for bus monitors will be provided over the summer.
 \item
  Bus monitors will be provided with apparel that aid in identifying them.
 \item
  \hspace{0pt}All bus monitors will be required to complete specific
  training, as outlined in Appendix AD.
 \item
  Should someone wish to bus monitor for an event during the year without completing the required training, they will be paired with someone that has completed the training. This is at the discretion of the event organizer

\end{enumerate}

\subsubsection{I.D.E.A. Committee (Inclusivity and Diversity in Engineering Alliance)}
\label{i.d.e.a.-committee-inclusivity-and-diversity-in-engineering-alliance}
\begin{enumerate}
 % \setcounter{enumi}{3}
 \item
  The Equity and Inclusion Officer shall chair the I.D.E.A. Committee.
 \item
  I.D.E.A. Committee will ensure that all voices and perspectives in the MES are being heard.
 \item
  This committee will facilitate communication between the WIE Society, NSBE, EngiQueers, AISES, and MEwD.
\end{enumerate}

\subsubsection{Conference Advisory Committee}
\label{conference-advisory-committee}
\begin{enumerate}
 % \setcounter{enumi}{3}
 \item
  The Vice-President External shall chair the Conference Advisory Committee.
 \item
  The committee will consist of all present chairs and co-chairs for upcoming successfully bidded upon or working conferences, and any voluntary past conference chairs from McMaster conferences.
 \item
  The committee will be used to share knowledge on conference logistics and more transparency on current conference going-ons.
\end{enumerate}
