\section{Board of Advisors Terms of Reference}
\label{board-of-advisors-terms-of-reference}

\begin{enumerate}
 \item
  Objective

  The Board of Advisors exists to provide strategic guidance and a thoughtful sounding board for the MES Executive and other MES members as appropriate.

  The Board of Advisors is a group of advisors, rather than a Board of Directors which aims to form consensus or decisions. Its powers will be limited to providing advice and recommending lines of action. The advice is available both as requested by the MES Executive and also by the Board of Advisors proactively contacting the MES Executive with ideas, leads, and opportunities.

 \item
  Membership

  Members shall be selected based on their position within a particular group (e.g. Faculty of Engineering)or based on their proven commitment and passion for the MES.

  Members may be asked to leave by the President if they fail to fulfill the responsibilities outlined within these terms of reference. If the Board loses a member due to job change or attrition, the President will prioritize filling this position with the appropriate candidate.

  The Board of Advisors shall be comprised of the following members:

  \begin{enumerate}
   \item
    Manager of Alumni Relations \& Youth Programs Office
   \item
    Any former MES President
  \end{enumerate}

  The Board of Advisors shall have the following ex-officio members:

  \begin{enumerate}
   \item
    The previous MES President
  \end{enumerate}

  Members of the board shall:

  \begin{enumerate}
   \item
    Be selected to provide the mix of expertise necessary to best guide the MES Executive towards the MES' Mission Statement.
   \item
    Serve in their individual capacity, regardless of their relationship with a specific group (e.g. their employer) for a renewable term of one year.
   \item
    Participate in at least one meeting per year.
   \item
    Be appointed solely by the MES President every year.
  \end{enumerate}

 \item
  Meetings

  Board of Advisors meetings shall:

  \begin{enumerate}
   \item
    Occur at least twice per year, typically once in each semester. One meeting will serve as a transition meeting with both incoming and outgoing MES Executive members present. Additional meetings may also be held under special circumstances.
   \item
    Be located on McMaster University campus if possible.
   \item
    Be organized by the Manager of Alumni Relations \& Youth Programs Office.
  \end{enumerate}

 \item
  Responsibilities

  The Board of Advisors will:

  \begin{enumerate}
   \item
    Meet with the MES Executive to review progress, address strategic questions, and plan for the upcoming year.
   \item
    Assist transitions between the incoming and outgoing MES Executives by maintaining knowledge throughout the years.
   \item
    Guide the MES Executive towards all of the MES' long-term goals.
   \item
    Represent the MES' best interests across campus and in industry.
   \item
    Act as stewards of the MES Mission Statement to help ensure that the MES Executive is appropriately advancing its mission.
   \item
    Engage in a reflective, self-evaluative process to improve board effectiveness.
   \item
    Act as a spokesperson on behalf of the MES, which could include being profiled on the MES website and in other communication as a Board of Advisors member.
   \item
    Declare any individual conflicts of interest to the MES President.
   \item
    Ensure the next meeting is planned at an appropriate time.
  \end{enumerate}
\end{enumerate}
% \end{document}
